Analyse from review

### 2021-04-30 manuscript/bef_stability/fig1_biomass_network.Rmd
Generate figures for talk

```{r}
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]

myload(metaweb_analysis,  dir = mypath("data"))
TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = sp_color[node_sp],
  abund = 1,
  collink="grey70",
  scale_abun = .005
) 
```

```{r}
```

@@

@@

``` 
```{r set-up}
st <- c(first_st$station[5], last_st$station[5]) 
library(viridis)
library(ggsci)
library(RColorBrewer)
display.brewer.pal(n = 8, name = 'Dark2')
display.brewer.pal(n = 8, name = 'Set2')

@@

>>>>

```{r}
myload(metaweb_analysis,  dir = mypath("data"))
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]

TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = sp_color[node_sp],
  abund = 1,
  collink="grey70",
  scale_abun = .005
) 
```

@@

map_alone <- p_st + 
  geom_sf(data = filter(station, type == "stable"), color = "black") +
  coord_sf(
    xlim = c(60000, 1100000),
    ylim = c(6100000, 7122216),
    datum = sf::st_crs(2154),
    crs = 2154,
    expand = FALSE
    ) +
  theme_void() +
  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")
save_plot(mypath("manuscript", "bef_stability", "figs/map_station.png"), map_alone,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 4,
  bg = "transparent"
)
ggdraw(map_alone)

@@

```

```{r set-up}
st <- c(first_st$station[5], last_st$station[5]) 
library(viridis)
library(ggsci)
library(RColorBrewer)
display.brewer.pal(n = 8, name = 'Dark2')
display.brewer.pal(n = 8, name = 'Set2')

@@

## Get a temporal network

```{r}
temporal_network_plot <- get_network_temporal_plot(net_list = network_analysis, station = st[2],
  selected_years = NULL,
  node_color = meta_node_color, scale_node_size = 0.05,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
temporal_network_plot <- map(temporal_network_plot,
  ~.x + theme(rect = element_rect(fill = "transparent")))
p_temporal_network <- plot_grid(plotlist = temporal_network_plot)

save_plot(mypath("manuscript", "bef_stability", "figs/temporal_network.png"),
  p_temporal_network,
  nrow = 3, 
  ncol = 4,
  base_height = 4,
  base_width = 4,
  bg = "transparent"
)
```

### 2021-04-30 manuscript/bef_stability/review_analysis.Rmd
Generate figures for talk

fr_border <- sf::st_as_sf(raster::getData("GADM", country = "FRA", level = 0))
debug(extract_nc_value)
climate_data = extract_nc_value(first_year = 1995, 
                                last_year = 2018,
                                local_file = FALSE,
                                file_path = NULL,
                                sml_chunk = "2011-2020",
                                spatial_extent = fr_border,
                                clim_variable = "mean temp",
                                statistic = "mean",
                                grid_size = 0.25,
                                ecad_v = NULL,
                                write_raster = TRUE,
                                out = "raster_mean_temp.grd",
                                return_data = TRUE)
# Get annual mean for each point 
annual_avg_temp_pnts = temporal_aggregate(x = rbk,
                                          y = sf_point,
                                          agg_function = "mean",
                                          variable_name = "average temp",
                                          time_step = "annual")
```

>>>>

fr_border <- sf::st_as_sf(raster::getData("GADM", country = "FRA", level = 0))
debug(extract_nc_value)
options(timeout=120)
climate_data = extract_nc_value(first_year = 1995, 
                                last_year = 2018,
                                local_file = FALSE,
                                file_path = NULL,
                                sml_chunk = "2011-2020",
                                spatial_extent = fr_border,
                                clim_variable = "mean temp",
                                statistic = "mean",
                                grid_size = 0.25,
                                ecad_v = NULL,
                                write_raster = TRUE,
                                out = "raster_mean_temp.grd",
                                return_data = TRUE)
# Get annual mean for each point 
annual_avg_temp_pnts = temporal_aggregate(x = rbk,
                                          y = sf_point,
                                          agg_function = "mean",
                                          variable_name = "average temp",
                                          time_step = "annual")
```
